Correspondence Analysis of Two Mode Networks

### 2025-01-27 analysis-R1.qmd
Ay caramba

# Setup
```{r setup}
   knitr::opts_chunk$set(include = TRUE, 
                       echo = FALSE, 
                       warning = FALSE, 
                       message = FALSE)
   library(conflicted)
   library(FactoMineR)
   library(here)
   library(igraph)
   library(kableExtra)
   library(networkdata)
   conflicted::conflicts_prefer(dplyr::filter)
```

# Southern Women Data Table
```{r HTML data table}
   g <- southern_women
   A <- as.matrix(as_biadjacency_matrix(g))
   p.ord <- c("EVELYN", "LAURA", "THERESA", "BRENDA", "CHARLOTTE", "FRANCES", "ELEANOR", "RUTH", "VERNE", "MYRNA", "KATHERINE", "SYLVIA", "NORA", "HELEN", "OLIVIA", "FLORA", "PEARL", "DOROTHY")
   A <- A[p.ord, ]
   rownames(A) <- c("EVELYN", "LAURA", "THERESA", "BRENDA", "CHARLOTTE", "FRANCES", "ELEANOR", "RUTH", "VERNE", "MYRA", "KATHERINE", "SYLVIA", "NORA", "HELEN", "OLIVIA", "FLORA", "PEARL", "DOROTHY")
   colnames(A) <- paste("E", 1:14, sep = "")
   kbl(A, align = "c", format = "latex", 
       booktabs = TRUE, linesep = "") %>% 
      kable_minimal(full_width = F, font_size = 10) %>% 
      save_kable(here("southern-women-corrected.tex"))
```

```{r}
   png(file = here("Plots", "ca-southern-women.png"), width=700, height=700)
   CA(A)
   dev.off()
```

@@

>>>>

# Setup
```{r setup}
     knitr::opts_chunk$set(include = TRUE, 
                       echo = FALSE, 
                       warning = FALSE, 
                       message = FALSE)
     library(conflicted)
     library(FactoMineR)
     library(ggcorrplot)
     library(ggplot2)
     library(here)
     library(igraph)
     library(kableExtra)
     library(networkdata)
     library(stringr)
     conflicted::conflicts_prefer(dplyr::filter)
```

# Southern Women Data Table
```{r HTML data table}
     A <- as.matrix(as_biadjacency_matrix(southern_women))
     rownames(A) <- str_to_title(rownames(A))
     colnames(A) <- str_replace(colnames(A), "/", "-")
     wlab <- paste("W", 1:18, sep = "")
     wlab <- paste(wlab, rownames(A), sep = " (")
     wlab <- paste(wlab, ")", sep = "")
     elab <- paste("E", 1:14, sep = "")
     elab <- paste(elab, colnames(A), sep = " (")
     elab <- paste(elab, ")", sep = "")
     rownames(A) <- wlab
     colnames(A) <- elab
     p <- ggcorrplot(t(A), colors = c("white", "white", "red")) 
     p <- p + theme(legend.position = "none", 
                  axis.text.y = element_text(size = 16),
                  axis.text.x = element_text(size = 16, angle = 45, hjust = -0.2),
                  )
     p <- p + scale_x_discrete(position = "top") 
     p <- p + scale_y_discrete(limits = rev)
     jpeg(file = here("Plots", "southern-women.jpg"), width=800, height=800)
     p
     dev.off()
```

```{r CA of affiliation matrix}
   ca.res <- CA(A, graph = FALSE)
   plot.dat <- data.frame(rbind(ca.res$row$coord, ca.res$col$coord)[, 1:2])
   plot.dat <- cbind(plot.dat, mode = c(rep(1, 18), rep(2, 14)), names = rownames(plot.dat))
   p <- ggplot(plot.dat, aes(y = Dim.2, x = Dim.1, 
                             color = factor(mode), label = names))
   p <- p + geom_vline(xintercept = 0, color = "gray")
   p <- p + geom_hline(yintercept = 0, color = "gray")
   p <- p + geom_text_repel(size = 4, max.overlaps = 50)
   p <- p + theme_minimal() 
   p <- p + theme(legend.position = "none",
                  axis.text = element_text(size = 18),
                  axis.title = element_text(size = 20)
                  )
   p <- p + labs(x = "Second Dimension", y = "First Dimension")
   p <- p + scale_color_manual(values = c('red', 'blue'))
   png(file = here("Plots", "ca-southern-women.png"), width=600, height=625)
   p
   dev.off()
```

@@

```{r CA versus Reflections Scatter}
   source(here("Functions", "TwoModeCA.R"))
   tm <- TwoModeCA(A)
   p.plot.dat <- data.frame(c = tm$ca.eigvec.r[, 1]*-1, r = a$p.s[, 26])
   p <- ggplot(data = p.plot.dat, aes(x = c, y = r))
   p <- p + geom_point(size = 3, color = "blue") 
   p <- p + geom_smooth(method = "lm", se=FALSE, formula = y ~ x, color = "gray")
   p <- p + geom_text_repel(aes(label = rownames(p.plot.dat)), color = "red")
   p <- p + theme_minimal() + labs(x = "First CA Dimension", y = "26th Reflection (Standardized)")
   p <- p + theme(axis.text = element_text(size = 16),
                  axis.title = element_text(size = 16))
   png(file = here("Plots", "p-ca-ref-corr.png"), width=600, height=625)
   p
   dev.off()

   g.plot.dat <- data.frame(cbind(c = tm$ca.eigvec.c[, 1]*-1, 
                                  r = a$g.s[, 26]))
   p <- ggplot(data = g.plot.dat, aes(x = c, y = r))
   p <- p + geom_point(size = 3, color = "red") 
   p <- p + geom_smooth(method = "lm", se=FALSE, formula = y ~ x, color = "gray")
   p <- p + geom_text_repel(aes(label = rownames(g.plot.dat)), 
                            color = "blue", size = 6)
   p <- p + theme_minimal() + labs(x = "First CA Dimension", y = "26th Reflection (Standardized)")
   p <- p + theme(axis.text = element_text(size = 16),
                  axis.title = element_text(size = 16))
   png(file = here("Plots", "g-ca-ref-corr.png"), width=600, height=625)
   p
   dev.off()
```
